Radioastronomical image reconstruction using Kalman filter under ionospheric perturbations

### 2022-08-07 article/article.tex
update

@@

	%Ainsi que la distance $d_2$ :
	In order to measure influence of a specific element, the ??? distance $d_2$ is the following :
	$$
	\forall(A,B)\in\left(\mathcal{M}_{m,n}(\mathbb{K})\right)^2\quad d_2(A,B) = \sum_{
		\mathclap{
			\substack{
				1\le i\le m \\1\le j\le n
			}
		}
	}\abs{A_{ij} - B_{i,j}}
	$$

@@

@@

	To further measure the effect of this error, it will be introduced on a single direction first, then on 5 directions, then on all of them.

@@

>>>>

	\newpage
	\part{SATIE}

@@

	%Ainsi que la distance $d_2$ :
	In order to measure influence of a specific element, the additive distance $d_2$ is the following :
	$$
	\forall(A,B)\in\left(\mathcal{M}_{m,n}(\mathbb{K})\right)^2\quad d_2(A,B) = \sum_{
		\mathclap{
			\substack{
				1\le i\le m \\1\le j\le n
			}
		}
	}\abs{A_{ij} - B_{i,j}}
	$$

@@

		\section{Data simulation and Image reconstruction}
	\subsection{Simulation}

	Data simulation will be done as stated in [REF TER]. First the visibilities matrix is computed using the reference image and the UV-plane of the antenna mesh. To simulate visibilities at different snapshots, we apply the wanted transformation without noise and use the same UV-plane matrix to compute visibilities.\\

	To add noise, a normally distributed random matrix is generated and the covariance of that matrix is added to the visibilities one. This matrix could also be directly generated using Wishart distribution. \\

	\subsection{Reconstruction}

	To obtain the initial image $\x_0$ two methods are used depending on the goal of the measure. \\

	When reviewing performances under certain errors, all other inputs of the filter - including $\x_0$ - must be errorless. The simplest way of doing that for $\x_0$ is to use the reference image as input. \\

	When reviewing Kalman filter performances under real conditions, the reference image is not considered as knwon, and we need to reconstruct the image from the visibilities matrix. While different methods exist [REF TER], the ones used here are MVDR reconstructions followed by Maximum Entropy deconvolution.

@@

	To further measure the effect of this error, it will be introduced on a single direction first, then on all of them.

@@

	\subsubsection{All directions}
